Hydras \& Co.

### 2023-07-02 doc/chapter-fol.tex
more documentation on FOL

Please note that the following constructions are parametrized with an
arbitrary language $L$, decared in the \texttt{ProofH} section.

@@

We want to define a data type  \texttt{Prf $l$ $F$}  of ``proof trees of the formula $F$, where $l$ is the list of assumptions used in the proof, enumerated left-to-right (\emph{i.e.} the fringe of the proof tree)''. 
Please note that this representation

@@

@@

@@

@@

\inputsnippets{FolExamples/eat}

\begin{todo}
Give examples in a toy language.

Give an example which motivates \texttt{SysPrf}:

@@

\subsection{Contexts as sets}

@@

>>>>

Please note that the following constructions are parametrized with an
arbitrary language $L$, declared in the \texttt{ProofH} section.

@@

We want to define a data type  \texttt{Prf $l$ $F$}  of ``proof trees of the formula $F$, where $l$ is the list of assumptions used in the proof, enumerated left-to-right (\emph{i.e.} the fringe of the proof tree)''.

@@

\subsubsection{Warning}

We won't respect the order in which \texttt{Prf}'s constructor 
are enumerated in \texttt{folProof.v}. We preferred to present 
these constructors in an order inspired by a sequence
 of simple examples. On the other hand, we didn't change this order in 
\texttt{folProof.v}, in order not to break complex proofs by pattern-matching.

See \href{https://en.wikipedia.org/wiki/List_of_Hilbert_systems}.

@@

Let $A$ and $B$ be two formulas on $L$, $\textit{Axm1}$
 and $\textit{Axm2}$ two sequences of formulas.
If we have 
two proof trees of respective types \texttt{Prf Axm1 $A\arrow B$} and  \texttt{Prf Axm2 $B$}, then we build a proof tree
for $B$ whose fringe is the concatenation of $s_{AB}$ and $s_A$.

@@

The following proof script is a quite naive application of 
\texttt{AXM} and \texttt{MP}.

@@

We can make this proof script shorter, using existential variables.

\inputsnippets{FolExamples/cutMP}

\inputsnippets{FolExamples/cutMP2}

\subsubsection{Hilbert's axioms for implication}

\inputsnippets{folProof/IMP12}

\inputsnippets{FolExamples/PrfEx3}

\begin{remark}
\label{sec:remark-on-hilbert-systems}
One may think that this proof 
is quite clumsy. \emph{Right}.
But we must recall that \texttt{Prf} is a basic Hilbert-like
proof system, which will make it easier to study.
In the next chapter, we will consider a derived proof system 
where the \emph{deduction theorem} will allow us to consider shorter and more natural proofs.
\end{remark}

\begin{exercise}[**]
  Is it possible to build a term of type
\texttt{Prf L [A] B -> Prf L [] (A->B)\%fol} ?
\end{exercise}

\subsubsection{The rule of contraposition}

The only rule about the \texttt{notH} connective is
the \emph{contraposition rule}.

\inputsnippets{folProof/CP}

The following script shows that \texttt{CP} entails the 
derived rule of \emph{proof by contradiction}.

\inputsnippets{FolExamples/PrfEx4}

\begin{remark}
Same remark as~\ref{sec:remark-on-hilbert-systems}.
\end{remark}

\begin{exercise}
  Replay this proof with pen and paper!
\end{exercise}

\begin{todo}
To do propositional connectives before FO (in the doc, but not 
 in the vernacular file)
To do : EQ1 before GEN

@@

%%%%%%%%%%%%%% New chapter 
\subsection{Contexts as sets}

@@

%%%%%%%%%%%%%%% New chapter!
